Delocalization of Eigenvectors in Random Matrices

### 2025-03-24 Draft.tex
somewhere along Thm 1

\begin{boxtheorem}{Theorem 1: (Stopping time).} $\mathbb{P}[\tau_{\text{stop}, i} \neq  1] \lesssim_D N^{-D}$ for any $i=1, 2$ and $D > 0$.
\end{boxtheorem}
\textit{Proof} - By Boole's inequality: $$\mathbb{P}\left[\tau_{\sto, 1}\neq 1\right]\leq \mathbb{P}[\left\{\tau_{\sto, 2}\neq 1\}\cap \{\tau_{\sto, 1=1}\}\right]+P[\tau_\sto=\tau_{\sto, 1}<1]$$
On the event of the left term, we have $|\E_{\tau_\sto}(z)_{ab}|\geq W^{\delta_\sto}W^{-3/4}\eta_t^{-1}W^{-1}\eta_t^{-1/2}$ by our ear

\subsection*{7.2 Theorem 2 - Quantum Diffusion}
\begin{boxtheorem}{Theorem 2: (Quantum Diffusion)}
For $|E|<2$ fixed, assume $\exists \nu>0$, s.t. $\eta \asymp W^2 N^{-2}$ and $W\geq W^{8/11+\nu}$. Then: $$\max_{x, y}|T_{xy}-\Theta_{xy}|\prec W^{-\frac{7}{4}}\eta^{-\frac{3}{2}}$$
\end{boxtheorem}
\textit{Proof} -

>>>>

\begin{boxtheorem}{Theorem 1: (Stopping time).} $\mathbb{P}[\tau_{\text{stop}, i} \neq  1] \lesssim_D N^{-D}$ for any $i=1, 2$ and $D > 0$.
\end{boxtheorem}
\textit{Proof} - By Boole's inequality: $$\mathbb{P}\left[\tau_{\sto, 1}\neq 1\right]\leq \mathbb{P}[\left\{\tau_{\sto, 2}\neq 1\}\cap \{\tau_{\sto, 1=1}\}\right]+\mathbb{P}[\tau_\sto=\tau_{\sto, 1}<1]$$
For any $\mathcal{A}\in \{\tau_\sto = \tau_{\sto, 1}<1\}$, we have $|\E_{\tau_\sto}(z)_{ab}|\geq W^{\delta_\sto}W^{-3/4}\eta_t^{-1}W^{-1}\eta_t^{-1/2}$. By definition of the stopped SDE, we have $\E_{\tau_\sto}(z) = \E_{\tau_\sto}^{\sto}(z)$, i.e: $$\mathbb{P}\left[\tau_\sto = \tau_{\sto, 1}<1\right]\leq \mathbb{P}\left[\max_{t\in [0, 1]}\max_{a, b}\frac{|\E_t^{M, \sto}(z)_{ab}|}{W^{-\frac{3}{4}}\eta_t^{-\frac{3}{4}}W^{-1}\eta_t^{-\frac{1}{2}}}\geq W^{\delta_\sto}\right]$$
By our theorems $6.1$ through $6.3$ in the last section applied to the RHS, we know from the definition of stochastic domination that for any $D>0$: 
$$\mathbb{P}\left[ \tau_\sto = \tau_{\sto, 1}<1\right]\leq C_DN^{-D}$$
Those same theorems imply that $$\max_{t\in [0, 1]}\max_{a, b}\frac{|\E_t^{M, \sto}(z)_{ab}|}{W^{\delta_\sto}W^{-\frac{3}{4}}\eta_t^{-\frac{3}{4}}W^{-1}\eta_t^{-\frac{1}{2}}}$$

\subsection*{7.2 Theorem 2 - Quantum Diffusion}
\begin{boxtheorem}{Theorem 2: (Quantum Diffusion)}
For $|E|<2$ fixed, assume $\exists \nu>0$, s.t. $\eta \asymp W^2 N^{-2}$ and $W\geq W^{8/11+\nu}$. Then: $$\max_{x, y}|T_{xy}-\Theta_{xy}|\prec W^{-\frac{7}{4}}\eta^{-\frac{3}{2}}$$
\end{boxtheorem}
\textit{Proof} - By the previous theorem and the definition of stopping time, we know that $$\max_{a,b}|\E_1(z)_{ab}|\prec W^{-\frac{7}{4}} \eta_1^{-\frac{3}{2}}$$
But recall by our flow construction that $\eta_1=\eta$ and by extension, $T_1=T$ and $\Theta_1=\Theta$, meaning that: $$\max_{a,b}|\E_1(z)_{ab}| =\max_{x, y}|T_{xy}-\Theta_{xy}|\prec W^{-\frac{7}{4}}\eta^{-\frac{3}{2}}$$
